\chapter{Related Work}
\label{cha:related-work}

This chapter defines the previous work related to the project and defines and describes the technologies and frameworks used within the project. While the project is built based on the technologies discussed within the scope of the course, the inspiration has been found while reviewing literature on applications of IoT technology specifically [ref Smart office energy management system using bluetooth low energy based beacons and a mobile app]. This has shown that simple BLE Beacons and mobile application can be used within building automation environment. Further experiments have been made in order to determine potential of wireless sensor networks and bluetooth technology to monitor refridgerated containers during transport[ref Review. Monitoring the intermodal, refrigerated transport of fruit using sensor networks]. Other competing radio technologies in the arena of wireless sensor networks have been discussed as well such as 802.15.4 and its usage within (among others) Zigbee technology. Bluetooth low energy has however advantage in its integration to most of the modern smartphones and the growth potential of the technology [ref https://www.statista.com/statistics/750569/worldwide-bluetooth-low-energy-device-market-volume/]. Its ready availability was a determining factor in choosing the technology for status broadcasting within this project. It is also expectable that the application will focus to more advanced use cases due to possibility of creation of a 6LoWPAN[ref] network over BLE system. It would be unfair not to mention very comprehensive book [ref Beginning Sensor Networks with Arduino and Raspberry Pi] on starting with wireless sensor networks and their applications. While the book does primarily consider Zigbee for networking the inspiration for building monitoring systems with data storage has had effect on the ideas behind the project. The project also considered on how to create a SCADA system (in our case very simple) for IoT based environment and mobile users. This have provided an interesting topic as the SCADA system of the future will have to be able to handle IoT environments [ref An IoT architecture for things from industrial environment] and will have to handle the current challenges of these systems especially in terms of security [ref Cloud-Assisted IoT-Based SCADA Systems Security: A Review of the State of the Art and Future Challenges], which we have not considered within our implementation.


Whereas the purpose of \autoref{cha:introduction} was to entice and
convince the reader that work reported is interesting, that the author
is asking the right questions about it, and reading about it will be
worthwhile, the purpose of \autoref{cha:related-work} is to
demonstrate that the author possesses a fine overview and keen
understanding of the topic of the work.  Note that while the title of
the chapter is ``Related Work'', it might as well be called
\emph{``Relevant} Work'' in that you should only include work that are
directly useful or relevant to your purpose. 

Writing about others' work can be challenging---it is easy to succumb
to just writing condensed summaries, which are just as tedious to read
as they are to write. A better method is to gain an overview over the
field of inquiry, and then establish in the first section the aspects
or dimensions that are crucial to systems or methodologies such as the
ones described. This demonstrates to the reader that the author has
understanding and judgement. Having done this, every paper or work can
then be described in those established terms. This makes for easier
and much more structured writing, and it also helps the reader
differentiate the systems and works reported on. If there are multiple
works that cover approximately the same area (\eg using the same
technique), you may mention several, but only go into detail with the
most significant or representative one.

The chapter can then be concluded with a table summarising all the
work reported on using the aspects defined in the introduction of the
chapter.

A crucial element of this chapter is that it concerns the work of
others and \emph{only} that. While the selection of aspects or
dimensions described above invariantly will reflect your own focus,
that should be the extend of which your own work and plans influence
this chapter.  Your own judgement comes in the next chapter.

\section{Frameworks and Technologies}
\label{sec:fram-techn}

Related work need not be only published academic work. In many cases,
it is also relevant to describe crucial frameworks and technologies
that will be used or are relevant for the thesis.  This does not mean
that all employed technologies should be described in detail, but
frameworks and technologies that are unusual (for lack of a better
word) could be described here. \Eg there is no need to describe an
ordinary network stack, but if the work involves GPU programming, a
description of the chosen architecture might well be relevant, as it
informs all the following chapters.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../ClassicThesis"
%%% End:
